Collapsed Cores in Globular Clusters, \\ Gauge-Boson Couplings, and AAS\TeX\ Examples

### 2014-02-27 tex/paper1/paper1.tex
more on the paper

The foregoing discusses the implications of red-noise power spectra
for the detection of narrow-frequency band oscillations when looking
at single time-series.  The advantage of AIA is that there is more
than one time-series to consider.  Evidence for the presence of a wave
in the corona is much stronger if it can be shown that a narrow
frequency-band oscillation occurs is significantly above a red-noise
background signal in several neighboring pixels.

>>>>

The foregoing discusses the implications of red-noise power spectra
for the detection of narrow-frequency band oscillations when looking
at single time-series.  The advantage of AIA is that there is more
than one time-series to consider.  Evidence for the presence of a wave
in the corona is much stronger if it can be shown that narrow
frequency-band oscillations occur significantly above a red-noise
background signal in several neighboring pixels.
